### 2015-02-27 icfp15-servo/browsers.tex
Add related browser research. Cleanups.

Modern web browsers do not just load static pages, but can also handle pages that have similar
complexity to native applications.
From application suites such as the Google Apps\footnote{\url{https://apps.google.com}} to games
based on the Unreal Engine\footnote{\url{https://blog.mozilla.org/blog/2015/02/24/unreal-engine-4-7-binary-release-includes-html5-export-3/}},
modern browsers have the ability to handle much more than simple static pages.
\figref{fig:browser} shows the steps in processing a site.
While the naming is specific to the Servo browser, similar steps are used in all modern browsers.\footnote{\url{www.html5rocks.com/en/tutorials/internals/howbrowserswork/}}
\begin{figure*}%[ht]
  \begin{center}
    \includegraphics[scale=0.7]{pics/browser}
  \end{center}%
  \caption{Processing stages and intermediate representations in a browser engine.}
  \label{fig:browser}
\end{figure*}%

@@

Whether through timers, \lstinline[language=HTML]{<script>} blocks in the HTML, user interactions, or other event handlers,
JavaScript (JS) code may execute at any point during parsing, layout, and painting or afterwards during display.
These scripts can modify the DOM tree, which may require rerunning the layout and painting passes in order to update
the output.
Most modern browsers use some form of dirty bit marking to attempt to minimize the recalculations during this process.

>>>>

Modern web browsers do not just load static pages, but can also handle pages that have similar
complexity to native applications.
From application suites such as the Google Apps\footnote{\url{https://apps.google.com}} to games
based on the Unreal Engine\footnote{\url{https://blog.mozilla.org/blog/2015/02/24/unreal-engine-4-7-binary-release-includes-html5-export-3/}},
modern browsers have the ability to handle much more than simple static pages.
\figref{fig:browser} shows the steps in processing a site.
While the naming is specific to the Servo browser, similar steps are used in all modern browsers.\footnote{\url{www.html5rocks.com/en/tutorials/internals/howbrowserswork/}}
\begin{figure*}[ht]
  \begin{center}
    \includegraphics[scale=0.7]{pics/browser}
  \end{center}%
  \caption{Processing stages and intermediate representations in a browser engine.}
  \label{fig:browser}
\end{figure*}%

@@

Whether through timers, \lstinline[language=HTML]{<script>} blocks in the HTML, user interactions, or other event handlers,
JavaScript code may execute at any point during parsing, layout, and painting or afterwards during display.
These scripts can modify the DOM tree, which may require rerunning the layout and painting passes in order to update
the output.
Most modern browsers use some form of dirty bit marking to attempt to minimize the recalculations during this process.

### 2015-02-27 icfp15-servo/intro.tex
Add related browser research. Cleanups.

\section{Introduction}
\label{sec:intro}
At the heart of a modern web browser is the browser engine, which is the code responsible
for loading, processing, evaluating, and rendering web content.
There are three current browser engine families:
\begin{enumerate}
\item Trident/Spartan, the engine in Internet Explorer
\item Webkit/Blink, the engine in Safari, Chrome, and Opera
\item Gecko, the engine in Firefox
\end{enumerate}
All of these engines have at their core many millions of lines of \Cplusplus code.
While the use of \Cplusplus has enabled all of these browsers to achieve excellent sequential
performance on a single web page, on mobile devices with lower processor speed but many
more processors, these browsers do not provide the same level of interactivity that they
do on desktop processors~\cite{parallelizing-web-pages,ZOOMM}.
Further, in an informal inspection of the critical security bugs in Gecko, we determined that
roughly 50\% of the bugs are use after free, out of range access, or related to integer
overflow.
The other 50\% is split between errors in tracing values from the JavaScript (JS) heap in the
\Cplusplus code and errors related to Just-in-time (JIT) code, which we will not discuss
further in this work.

>>>>

\section{Introduction}
\label{sec:intro}
At the heart of a modern web browser is the browser engine, which is the code responsible
for loading, processing, evaluating, and rendering web content.
There are three current browser engine families:
\begin{enumerate}
\item Trident/Spartan, the engine in Internet Explorer~\cite{IE}
\item Webkit\cite{WEBKIT}/Blink, the engine in Safari~\cite{SAFARI}, Chrome~\cite{CHROME}, and Opera~\cite{OPERA}
\item Gecko, the engine in Firefox~\cite{FIREFOX}
\end{enumerate}
All of these engines have at their core many millions of lines of \Cplusplus code.
While the use of \Cplusplus has enabled all of these browsers to achieve excellent sequential
performance on a single web page, on mobile devices with lower processor speed but many
more processors, these browsers do not provide the same level of interactivity that they
do on desktop processors~\cite{parallelizing-web-pages,ZOOMM}.
Further, in an informal inspection of the critical security bugs in Gecko, we determined that
roughly 50\% of the bugs are use after free, out of range access, or related to integer
overflow.
The other 50\% is split between errors in tracing values from the JavaScript heap in the
\Cplusplus code and errors related to dynamically compiled code.

### 2015-02-27 icfp15-servo/open.tex
Initial commit
Add related browser research. Cleanups.

\section{Libraries and abstractions}
\label{sec:libraries}

>>>>

\section{Open}
\label{sec:open}
While this work has discussed many challenges in browser design and our current progress,
there are many other interesting open problems.

\paragraph{Just-in-time code} is produced from all modern JavaScript engines in order to
dynamically produce native code that is intended to execute more efficiently than an
interpreted strategy.
Unfortunately, this area is a large source of security bugs.
These bugs come from two sources.
First, there are potential correctness issues.
Many of these optimizations are only valid when certain conditions of the calling
code and environment hold, and ensuring the specialized code is called only when those
conditions hold is non-trivial to verify.
Second, dynamically producing and compiling native code and patching it into memory
while respecting all of the invariants required by the JavaScript runtime (e.g., the
garbage collector's tracing hooks or free vs. in-use registers) is also a challenge.

\paragraph{JavaScript object rooting} is a problem related to objects from the JavaScript
heap that are held onto by \Cplusplus object --- and sometimes vice-versa.
Today, all modern engines manually manage the boundary code to handle tracing
these objects, and this leads to leaking objects or, worse, freeing objects that
are still in use.
The lack of a typical garbage collector for these objects also means that cycles
between \Cplusplus and JavaScript need to be broken through ad-hoc means.
